prophet ir trumpas conclusionas

### 2023-05-22 Prophetas ir trumpas conclusionas.Rmd
.

---
title: "prophet ir trumpas conclusionas"
output:
  pdf_document: Energy Trade Forecast
  html_document: default
date: "2023-05-21"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

>>>>

---
title: "prophet ir trumpas conclusionas"
output:
  html_document: default
  pdf_document: Energy Trade Forecast
date: "2023-05-21"
---
